Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-08-29 ms/main.tex
Add woodcock2006significance to the discussion

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$; or 
	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat{\gamma_1}<c<\hat{\gamma_2}$; or
  if \emph{viib} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$.
\end{enumerate}
\end{result}

@@

>>>>

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
  if \emph{(v)} $T_A>T_B$ and $\hat{\gamma_1} < c < \hat{\gamma_2}$; or 
	if \emph{(vi)} $T_A<T_B$ and $c>\hat{\gamma_1}$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
  if \emph{(viia)} $T_A < T_B$ and $v<\hat{v}$ and $\hat{\gamma_1}<c<\hat{\gamma_2}$; or
  if \emph{(viib)} $T_A < T_B$ and $v>\hat{v}$ and $c>\hat{\gamma_1}$ and $c>\hat{\gamma_2}$. %$0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
  if \emph{(viii)}  $T_A>T_B$ and $c > \hat{\gamma_2}$ and $v>\hat{v}$.
\end{enumerate}
\end{result}

@@

\citet{woodcock2006significance} showed the importance of non-vertical transmission for the evolution of cooperation. In their model the individuals interact according to standard prisoner dilemma game.
However, they do not link between interaction and transmission. In terms of our model they have choosen the assortative meeting coefficient $\alpha$ to be zero. Our results are more general since it shows the importance of assortative meeting for the evolution of cooperation.
